data exploration

### 2021-04-20 outputs/exploratory.Rmd
first draft complete

>>>>

```{r causaldiagram2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Diagram of desired causal sequence"}
mermaid("
graph LR
A{intervention}-->|1|B[student similarity perception]
A-->|2|C[instructor similarity perception]
B-->|3|D[ISR]
C-->|4|D[ISR]
D-->|5|E(grades)
D-->|6|F(persistence)
E-->|7|F
")
```

```{r}
studentfirstsimilaritymodel <- lm(data = expdata,
                                  formula = s1_sim ~ treatment + n_course + teacherid,
                                     na.action = na.omit)
studentsecondsimilaritymodel <- lm(data = expdata,
                                   formula = s2_sim ~ treatment + n_course + teacherid,
                                     na.action = na.omit)
studentsecondrelationshipmodel <- lm(data = expdata,
                                     formula = s2_tsr ~ treatment + s1_tsr + n_course + teacherid,
                                     na.action = na.omit)
teachersecondrelationshipmodel <- lm(data = expdata,
                                     formula = t2_tsr ~ treatment + n_course + teacherid,
                                     na.action = na.omit)
grademodel <- lm(data = expdata,
                 formula = grade ~ treatment + s1_female + ir_f16_gpa + n_course + teacherid,
                                     na.action = na.omit)
examgrademodel <- lm(data = expdata %>% filter(obj_exam == 1),
                     formula = t2_finalexam ~ treatment + s1_female + ir_f16_gpa + n_course + teacherid,
                                     na.action = na.omit)
teachersecondsimilarity <- polr(formula = as.factor(t2_sim1) ~ treatment + teacherid,
                                data = expdata,
                                Hess = TRUE,
                                     na.action = na.omit)

stargazer(studentfirstsimilaritymodel,
          studentsecondsimilaritymodel,
          studentsecondrelationshipmodel,
          teachersecondrelationshipmodel,
          grademodel,
          examgrademodel,
          teachersecondsimilarity,
          omit = c("teacherid"),
          omit.labels = c("Instructor fixed effect"))
```
